\acknowledge{%Thanks go here.
Thanks to my patient wife Amanda, walk-deprived dog Flora, loving family, and supportive friends for everything I have been able to accomplish.
%
I would not have been able to make it this far without you. 
%
Extra thanks to everyone in the Jaramillo lab for your friendship and help along the way. 
%
You have all been wonderful to work with, and I have learned a lot from you. 


Thank you to Santiago for your tireless help and patient guidance as I worked my way through many problems.
%
And thank you as well for teaching me to write good docstrings for my functions, and to write a wiki page whenever an issue requires multiple steps to solve.
%
Both have been invaluable when going back to see what I did to solve a problem in the past. 

I am also extremely lucky to have had the help of each of my committee members, both in guiding my work at UO and helping me find my path after.
%
The ION community has been kind yet rigorous in their evaluation of my work, generous with their time, and has instilled in me a great curiosity about the way the brain works. 


I never thought, back when I was characterizing populations of seaweed, or trawling for benthic fish down in Humboldt bay that I would end up spending my days trying to figure out how the brain enables us to learn, and to behave in a flexible manner in the face of a changing world. 
%
But ION took me in, and showed me the way.
%
And for that, I will be forever grateful.

%Leave an extra space before the final curly bracket. At least for me I had some strange problem where the last line became single spaced if I didn't.
}

